Presentation Materials

### 2017-03-19 San Antonio/presentation_materials.Rmd
more complete fixed effects

>>>>

### Fixed Effects Model with Combined Data (training = testing)

```{r fe.cmb}
if (!exists("fe.cmb.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(fe.cmb.result %>% filter(year >= 2005) %>% arrange(desc(num.death)), 20) %>% select(
  mine.name, num.death, severe, prob, pred
)
print(fe.cmb.performance)
```

### Fixed Effects Model with Divided Data (half training, half testing)

```{r fe.div}
if (!exists("fe.div.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(fe.div.result %>% filter(year >= 2005) %>% arrange(desc(num.death)), 20) %>% select(
  mine.name, num.death, severe, prob, pred
)
print(fe.div.performance)
```

### Logistic Regression Model without Fixed Effects

```{r glm}
if (!exists("glm.result")){load("./San Antonio/output/results_fixed_effects.RData")}
head(glm.result %>% filter(year >= 2005) %>% arrange(desc(num.death)), 20) %>% select(
  mine.name, num.death, severe, prob, pred
)
print(glm.performance)
```
